Ripple Consensus Review

### 2015-04-20 paper.tex
flesh out attacks

@@

\section{}

>>>>

how exactly does the skiplist work?

\subsection{Consensus}

@@

what happens with UNL majority is not reached?

\section{Attacks}

reference c3 criteria?

big picture with attacks is there is not a minimum cost to them unlike PoW

evaluate attacks for denial-of-service and theft potential; evaluate minimum
cost to carry out attack; possible minimum manpower to carry out attack

Type of attack: DoS and/or theft

Minimum cost: $0, $1k, $10k, $100k

Scope: targetted, broad, global
Duration: hours, days, weeks, indefinite - How long will it take to fix the bug?

we don't attempt to put a dollar figure on harm done, as depends enormously on
how people use ripple

\subsection{Consensus Split}

1) exploit consensus failure.

DoS: Cost \$0, Scope: global, Duration: hours
Theft: Cost \$1k, Scope: varies, Duration: hours

not as synergistic with other attacks; obvious flaw that will be fixed;
time-limited attack

\subsection{Scalability}

DoS: Cost \$100k, Scope: global, Duration: weeks

simply produce a lot of txs, paid for via fees, either covertely or overtly.
System will fail, guaranteed.

\subsection{UNL: Jurisdictional}

DoS/Theft: Cost \$100k, Scope: varies, Duration: indefinite

centralization attack - legal attack against centralized UNL. note
jurisdictional issues with delegating consensus to UNL

biggest issue is how can ripple compete against systems without the global
consensus req? if I'm a bank in russia, why use ripple when it opens me to UNL
issues?

\subsection{Software backdoor}

DoS/Theft: Cost \$0, Scope: varies, Duration: varies

mention unsigned code here

\subsection{UNL: key theft}

prep: Cost \$0, Scope: global, Duration: N/A

Gain control of UNL signing keys through theft/compromise.

\subsection{History simulation}

Theft: Cost \$0, Scope: targetted, Duration: weeks

from proof-of-stake terminology; simulated history is costless as no work
expended.

use backdoored software as example of how this can happen; also can happen with
jurisdictional attacks

if rippled sees two versions of history, what happens?

rewrite history attack - note lack of cost to rewrite because no PoW; single
implementation so likely we can hack all nodes at once

proof-of-work has a hard bound on rewrite attacks, because can't break laws of
physics

can talk about how cost to do a simulation attack is PoW $/targets; talk about slasher rule

\section{Synergistic Attacks}

do a directed graph of likely synergistic attack sequences
